Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2023-03-03 manuscript/manuscript.qmd
Use correct figure chunk names

Before exploring whether COVID-induced derogations are associated with specific human rights abuses, it is useful to examine how derogating and non-derogating states approached the implementation of their emergency public health measures. @fig-preds-prelim-1 shows the results of five logistic regression models as predicted probabilities of imposing specific emergency measures over the course of the first 15 months of the pandemic. In every case, throughout the early pandemic, countries with a formal derogation in effect are far more likely to have undertook each policy, and the difference in probabilities between derogating and non-derogating states is substantial (see @fig-preds-prelim-2 for the percentage-point differences between the predictions for the two groups of states).

>>>>

Before exploring whether COVID-induced derogations are associated with specific human rights abuses, it is useful to examine how derogating and non-derogating states approached the implementation of their emergency public health measures. @fig-preds-mfx-prelim-1 shows the results of five logistic regression models as predicted probabilities of imposing specific emergency measures over the course of the first 15 months of the pandemic. In every case, throughout the early pandemic, countries with a formal derogation in effect are far more likely to have undertook each policy, and the difference in probabilities between derogating and non-derogating states is substantial (see @fig-preds-mfx-prelim-2 for the percentage-point differences between the predictions for the two groups of states).
